\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{
\textit{When I look back on resolutions of improvement and amendment which have year after year been made and broken, either by negligence, forgetfulness, vicious idleness, casual interruption, or morbid infirmity; when I find that so much of my life has stolen unprofitably away, and that I can descry by retrospection scarcely a few single days properly and vigorously employed, why do I yet try to resolve again? I try because reformation is necessary and despair is criminal.} \newthought{- Samuel Johnson}}

\nolinenumbers
I'm a tech guy, so I see my life as a long download.
A long movie that I can watch as I'm downloading it.
If I live to 100, then I am currently 22\% finished.
I hope the file will pass 23\% and not buffer nor crash.
They say ``Life begins at 40'', so my mind can rest when the play reaches 40\%.
We are 8 billion plays being downloaded at once.
We are the actors and the audience built by God to make Him smile.
He might have other actors on other planets in this our Marvel cinematic universe.
I don't know if the movie with my name is comedic or tragedic.
I don't know if the play is mine to make, or if the choices have been pre-made.
But I know it's a good play. 
Else He wouldn't make it. 
Nor make me make it. 
Nor watch it himself. 
Nor let it play out in the background.
I don't know the ending.
But I hope it's a twist nobody saw coming except me. 
If I'm being honest, I would be even happier if it was a twist I didn't see coming.
The Christians say there's a post-credit scene, and I want to believe them.
\vspace{0.55cm}
I'm just excited to reach 99\% so that the credits will start rolling.
\linenumbers