\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}
\nolinenumbers
\begin{fullwidth} 
\footnotesize{
\begin{FlushRight}
{\textit{
\hspace{10em}Born in May 1917, John Bumpass Calhoun was an American ethologist and behavioral researcher. He believed that overpopulation could threaten the future of the human race. His studies in population density and its effects on behavior resulted in his Big idea: Behavioral Sink.

\hspace{10em}The term behavioral sink describes a collapse in behavior that can result from overcrowding. The initial hypothesis of John B. Calhoun was simple. He believed that when the population increases in a limited space. This leads to social breakdown.

\hspace{10em}To showcase this, he conducted a series of experiments with rats. The idea was to create ``rat utopias'' - ``enclosed spaces in which rats were given unlimited access to food and water, enabling unfettered population growth.'' The only adversity was the limit on space.

\hspace{10em}Initially, the rat population grew at a rapid rate. Doubling every 55 days. However, that changed on day 315. The population growth dropped significantly - doubling every 145 days. 

\hspace{10em}Also, there was a breakdown in the social structure. Some of the changes in behavior were the following: Inability for males to maintain their territory; Young were expulsioned before weaning was complete; Aggressive behavior of females; Wounding of young rats; Increase in homosexual predisposition.

\hspace{10em}After day 600. The social breakdown continued and permanently changed. The population declined toward extinction. Females ceased to reproduce, while males withdrew completely from all social interactions. They were mainly engaged in solitary pursuits - eating, sleeping, and self-grooming.

\hspace{10em}The conclusion from this experiment was that when all space is taken. When all social roles are filled. The stress experienced by the individuals in that narrow space will result in a total breakdown in complex social behaviors. Eventually, resulting in the demise of the population.}
\newthought{- John B. Calhoun}}
\end{FlushRight}}
\end{fullwidth}

\linenumbers

I want to buy an illegal gun for self-defence, 
I don't have the time to wait for the legal bullshit process
I want it now.\ I have the dime.
The CZ 75 pistol costs a handful, 
but is cheaper than a TEC-9.
Why am I buying?\ Because I will go out fighting.
Kidnap me?\ Fuck a ransom!\ Take 15 hits and then some
Fuck a handsome melee, I'll fuck up a robber's payday!
Fuck what the government says.
My life, my way!!\ldots
I will obviously buy a portable gun safe for it, I'm not insane.
Or else, someone would find it and assume I do usually partake in the business of smoking cocaine.
\vspace{0.4cm}