\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{Isn't it strange
That princes an' kings,
    And clowns that caper
    In sawdust rings,
    And common people
    Like you and me
    Are builders for eternity?
\hspace{-1em} Each is given a bag of tools,
    A shapeless mass,
    A book of rules;
    And each must make-
    Ere life is flown-
    A stumbling block
    Or a steppingstone.}
    \newthought{- R. L. Sharpe}}

\nolinenumbers

\newthought{- Marvelene}
\textit{\textbf{I'm not fine. } \sout{I'm not. I haven't been feeling well. I know I need to see the doctor. Who knows, there might be a cancerous cell hiding somewhere. I refuse to die yet. I still have so much to do for my folks. I've been pulling all nighters simultaneously. I'm probably -10kg by now. I know it's my choice and all, but I wish someone would check on me like a baby. Of course I'm an adult, but I guess I'm still a child. The one person I want to talk to anytime keeps getting busier and busier. And sleeps when he's not. Why am I feeling lonely these days? I shutdown my WhatsApp cos the only person I chat with no longer chats with me. It's messing me up, my expectations met with disappointments. So I decided. I'll reduce the attention I give to him, to increase the one I give to my improvement. It's like I'm taking a page out of his book, so he'll understand. At the end of the day, I have to provide for myself. I have to work for me and my family, and lookout for them. God knows I hate being a burden, and I was never really interested in getting attached to someone. Shit happened. The doing list was not for created for me in the first place. Tis to Maria, and for him. Does he think it's the same thing as texting me? Surely not. When he wakes up, the doing list. It's now the doing list. It used to be different. After the doing list for a day, he falls asleep. What do I get? Poems. Mostly. I want to be asked how I'm feeling. Cos I'm actually not fine. I prefer him calling, cos unlike me, he can't leave what he's doing to pay attention to me. Divided attention. Distracted. It's frustrating, with the bad network too. When I call, I easily lose the vibe these days. Before I call, I'm really excited. On the call, I gradually lose it. I no longer remember exciting topics. Can I actually survive without talking to him? Surely not. I'm just reducing my attention for the purpose of self-improvement. What's the use telling him all these..... It'll just repeat itself later. I know if I die before him, I'll become a distant fond memory. He'll have to remarry, or marry someone else, he's the first son an all. What am I typing? Is it my nature to mess up the good things in my life? My eyes are leaking. I actually feel lonely. I should put this energy to coding. Do I even have this energy? My hands shake occasionally, my chest hurts, my legs are weak. I'm getting weaker. A part of me hopes he reads this, a part of me doesn't. I love him so much. The urge to reopen WhatsApp is really strong right now. I'm going back to work.}}

\linenumbers
