\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{A man is great not because he hasn't failed; a man is great because failure hasn't stopped him.} \newthought{- Confucius}}

\textit{[MARVELENE]}
\resetlinenumber[1]Dear father, I am sure it is my duty to break the silence on my dealings;
There is a Gentleman of this town, named Pengk, for whom I have feelings.
He is a Youth Corper with a firm foundation, no pun intended, a Civil Engineer.
He is a Deltan 23-year-old Christian, and over our months we have grown near.
I am aware of my high opinion of his character and circumstance,
But I assure you, Sir, I have given him no blessed assurance.
I seek not to conceal from you a worthy affair's beginnings
I live in obedience to my parents, and I persevere to hear your preference.


\vspace{0.4cm} \textcolor{gray}{\rule[2.5mm]{7.4in}{0.4pt}}
\nolinenumbers
\begin{fullwidth}
\underline{\textit{Marvelene's Letter To Prof.~Dada}}
\vspace{0.4cm}
Good morning Dad.\ How was your night?
\vspace{0.4cm}
Since I can better express myself in writing, I decided to text you.
\vspace{0.4cm}
Dear father, There is a gentleman in this town, for whom I have feelings.
This is my first and only relationship, and we both started it with a purpose - to spend our future together.
He is a Youth Corper, a Civil Engineer(M.Sc).\ He studied at the UK. He's from Delta state, a Christian.
\vspace{0.4cm}
I gave us two years before marriage, because I concluded that we both need to find our footings after this phase called 
Youth Service.\ I also think it's too early to meet my parents, so I blocked him.
I'm getting to know his parents first, I've met his mother in Abuja here a few times.
\vspace{0.4cm}
I know that glistening gold is eye-catching, but Dad, I don't see happy Inokarare in that marriage. 
I like to think my happiness is the topmost priority. 
I already fasted and prayed to God about it, and I got this message: Last year, I asked God to send me someone that fits 
me, a good person that's inline with my moral values, because it looked like I had a closed-off heart and wealth couldn't 
even attract me.
\vspace{0.4cm}
Then I met this person, he was my friend for a while, and I studied him.
And I thought, ``Wow, he's a treasure''.\ I didn't tell that to him though, and he later expressed his feelings.
Why let go of a good thing you've been waiting for, when it eventually comes to you? 
\vspace{0.4cm}
I am aware of my high opinion of his character and circumstance, but I wish you can understand and trust me. 
Of course, nobody knows the future, we only live by the grace of God. 
And I pray that every event and outcome is according to God's will.
\vspace{0.4cm}
Let ME bring my husband to meet you, when the time is right.\ Please.
\end{fullwidth} \linenumbers