\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{Shabbat shalom to the army.}}

Be careful what you wish for, unless it lasts for one Freaky Friday.
Because you might just get it, and not love the prices you have to pay.
I am fine with the fines that are associated with being me.
To redesign my life on a whim may attract the bigger daily fee.
The `perks' are perky for one week, and the `nots' stay downright awful.
If it ain't broke, don't replace it with a smoother, faster model.
I do what I want when I want it, with a strong mind and body.
I love this life, and this my wife is a perfectly balanced deity.

\begin{comment}

\textit{[TO THE ARMY]}
\nolinenumbers
\begin{fullwidth}

\hspace{0.4cm}1.\ The application is free, and I am early to apply.
2.\ I am a Nigerian; as defined in the constitution of the Federal Republic of Nigeria.
3.\ I am a male at an age of 23 years.
4.\ I am medically, mentally and physically fit according to NA standards.
5.\ I have allies; 3 recognisable referees can recommend and attest to my good character.
6.\ I grew up in a Police Barracks, and attended a Catholic Boarding School.
7.\ I am disciplined, and I understand chain of command.
8.\ I measure in height above 1.85 meters
9.\ I measure in weight below 95kg.
10.\ I can run a mile in less than 10 minutes.
11.\ I can do more than 160 sit-ups, 80 squats, 40 push-ups, 20 pull-ups, and 10 dead-lifts.
12.\ I can swim a mile in less than 30 minutes.
13.\ I groom my hair and nails to be short, and I dress appropriately, just in case of physical altercations.
14.\ I am not a bully.
15.\ I don't have anger issues.
16.\ I am not a work-dodger.
17.\ Survival of the fittest has kept me busy all my life.
18.\ I have neither been trialed nor convicted by any court of law.
19.\ I am a Civil Engineer, B.Eng.~\& M.Sc.~from the University of Sheffield, with experience in Project Management.
20.\ I am most likely to succeed in this complex, creative, and rapidly-changing job.
21.\ We can lay a strong-enough foundation for our descendants to prosper.
22.\ I desire to fight for my fatherland.
23.\ The Army will pay me some assets which I will share in my last will and testament.
24.\ I have put my affairs in order so my family would be less hurt if and when I die.
25.\ I am not motivated by wealth, wine, or women.
26.\ I am experienced in battle, prepared for the terrors of the night.
27.\ I have never let off a stray bullet.
28.\ If there was a war then we could prove that we're worth more than anyone could expect.
29.\ I'm betting on Nigeria.
30.\ I intend to realise Rtd.~Obasanjo's vision for a developed united Nigeria.
31.\ I am religious enough to cherish human life.
32.\ I am utilitarian enough to take human life for defence.
33.\ The Executive Arm has a monopoly on Force, so who dares stand in our way.
34.\ I pledge to Nigeria, my country.\ To be faithful, loyal, and honest.\ To serve Nigeria with all my strength.\ To defend
\phantom{34. }her unity, and uphold her honor and glory.\ So help me God.
35.\ I am currently a National Youth Service Corps member serving at Setraco, in Life Camp, Abuja.
36.\ I've received recognition as a Corps Camp Director for my exemplary character.
37.\ On multiple occasions recently, I have been bestowed with the title of `Teacher'.
38.\ I possess an Intelligence Quotient between 120 and 130.
39.\ When I enter rooms, I used to look for the nearest exit; so I could run from suspects if I hear a loud noise.
40.\ Now, when I enter a room, I look out for suspects; so I can run towards the suspects to protect the innocent.
41.\ I can speak, hear, read, and write Mandarin Chinese.
42.\ I know the NATO phonetic alphabet memorised for spelling names over the phone.
43.\ My exposure to some of the global community has made me more patriotic to Nigeria - more than ever before.
44.\ Joining the military may strengthen my level of patriotism.
45.\ Firstborn kids (like me) have been proven more likely than younger siblings to have certain personality traits for grit.
46.\ Nobody can break me.\ My body would quit before my mind does.
47.\ I am not suicidal, but I can jump on a grenade for my band of brothers.
48.\ I like when my presence has a positive impact on a person.
49.\ People are complaining of bad governance.
50.\ I am putting my money where my mouth is; when I say that good governance is possible.
51.\ I am putting my hard-earned wisdom up for public scrutiny.
52.\ I may meet many like-minded people.
53.\ I have hunted and killed animals for food.
54.\ I have gardened and gathered forage for food.
55.\ It's a confidence boost.
56.\ I can hold my breath for 3 minutes.
57.\ I can go without water for 3 days.
58.\ I can go without food for 3 weeks.
59.\ I take the initiative to receive orders given and deliver results.
60.\ Military discounts.
61.\ The military is not going to be dissolved.
62.\ I can drive Automatic and Manual transmission cars.
63.\ I can ride a bicycle.
64.\ I am willing and able to learn to swim.
65.\ I know what I am up against and what I can expect.
66.\ I desire to offer my time in selfless service.
67.\ The relatively unrestricted movements on land, air, and sea.
68.\ I won't mind wherever I have to go.
69.\ I literally want to join, and I'm beckoning for your approval.
70.\ The Army is more than just a job; it is our first line of defence to protect our local population from potential threats.
71.\ I don't want to be the smartest person in any room.
72.\ Public service seems to be calling me.
73.\ I have seen some injustice in Nigeria that announced itself as `in need of repair'.
74.\ Bitches would let me autograph their breasts.
75.\ If I were one of 100 people in a room, I would be less agreeable than 82 of them and more agreeable than 17 of them.
76.\ If I were one of 100 people in a room, I would be more compassionate than 66 of them and less compassionate than
\phantom{76. }33 of them.
77.\ If I were one of 100 people in a room, I would be less polite than 98 of them and more polite than 1 of them.
78.\ If I were one of 100 people in a room, I would be more dutiful than 80 of them and less dutiful than 19 of them.
79.\ If I were one of 100 people in a room, I would be more industrious than 50 of them and less industrious than 49 of
\phantom{79. }them.
80.\ If I were one of 100 people in a room, I would be more orderly than 93 of them and less orderly than 6 of them.
81.\ If I were one of 100 people in a room, I would be more extraverted than 84 of them and less extraverted than 15 of
\phantom{34. }them.
82.\ If I were one of 100 people in a room, I would be more enthusiastic than 92 of them and less enthusiastic than 7 of
\phantom{34. }them.
83.\ If I were one of 100 people in a room, I would be more assertive than 63 of them and less assertive than 36 of them.
84.\ If I were one of 100 people in a room, I would be lower in neuroticism than 75 of them and higher in neuroticism
\phantom{34. }than 24 of them.
85.\ If I were one of 100 people in a room, I would be higher in withdrawal than 41 of them and lower in withdrawal
\phantom{34. }than 58 of them.
86.\ If I were one of 100 people in a room, I would be less volatile than 85 of them and more volatile than 14 of them.
87.\ If I were one of 100 people in a room, I would be higher in openness to experience than 80 of them and lower in
\phantom{34. }openness to experience than 19 of them.
88.\ If I were one of 100 people in a room, I would be higher in intellect than 72 of them and lower in intellect than 27 of
\phantom{34. }them.
89.\ If I were one of 100 people in a room, I would be higher in openness than 80 of them and lower in openness than 19
\phantom{34. }of them.
90.\ I have other career options, and I've weighed their pros and cons before choosing you.
91.\ I am ultra loyal.
92.\ I am verbose yet succinct; arrogant yet persuasive.
93.\ My country's economy is increasingly stalling.
94.\ I will do the best I can in service, and will not brag about it.
95.\ I don't have a social media presence so there's little chance of identity theft.
96.\ I am standing on the shoulders of heroes past who fought for the notion of a nation we now get to build.
97.\ We are making history; so right now, the future have their eyes on us.
98.\ I am Pengk Nnamdi Emmanuel Sylvester.
99.\ I am not throwing away my shot.
100.\ My partner Inokarare Marvelene Odey-Osha is joining me to lead.
101.\ \textit{Oorah}!
\end{fullwidth}

\vspace{-1.5em} \linenumbers

\end{comment}
