\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{Being a writer is signing up to have homework for the rest of your life.} \newthought{- Lawrence Kasdan}}

{\HUGE \theexcluded\ Drafts} \stepcounter{excluded}

BULLET #1 - Be on time.\
Time is the most precious possession.\
“Success” is spending the littlest time possible doing things you hate doing.\
Be smart with your time.\
Streamline, automate, and batch all recurring processes. Aim to have fun with everything you do and everything you make.\
When on-the-clock, total focus on the task-at-hand is required.\
When off-the-clock, spend time be vigilant to your personal well-being.\
It’s not about showing up at a certain hour. It’s about being fully where you are, when you are.\
Maintain your body: get 8 hours (or more) of sleep, drink 2 liters (or more) of water, and follow a nutritious diet.\
Maintain your mind: exercise, meditate, and socialize daily.\
\
BULLET #2 - Make things you would want to consume.\
If someone chooses to start their day with your brand, it should benefit them.\
To do this, there are two steps.\
Step one: chase your own curiosities, go on a mission, explore what pissed you off, or solve a problem.\
Step two: tell a quickly-paced, clear, concise story of your findings.\
Take the boring parts and make them simple to understand.\
Take the intimidating parts and make them entertaining. Ideas that are insightful, funny, or plain stupid are all acceptable.\
Don’t waste their time (refer back to Bullet #1).\
\
BULLET #3 - Make things no one else can make.\
You must have absolute willingness to be honest.\
Your natural quirks, goofiness, and eccentricities are exactly what makes you unique.\
Originality is encouraged when posing questions, conducting experiments, and communicating ideas. Oversharing is NOT allowed. Set clear lines for privacy and never overstep these lines. Trust your gut. Use your intuition; its wisdom has been built through years of experiences you didn’t know you were having. If your work seems wrong, you’re making the wrong environment.\
\
BULLET #4 - Maintain a calendar.\
Do NOT rely on memory recall for new ideas or tasks. When a new idea or task is born, enter this onto the master calendar immediately.\
When a new idea or task is completed or deemed unnecessary, it should be deleted from this calendar.\
There should be a maximum of three tasks per day, including one FROG, one ADDITIONAL, and one FUN.\
A “FROG” is defined as the most important task of the day. “Sit in the chair” until it is completed.\
An “ADDITIONAL” is the second-highest prioritized task. Do this once the FROG is complete. The “FUN” task should only be enjoyed once the other two tasks have been completed.\
\
BULLET #5 - Improve 1% with everything you create. Address the weakest links to improve the baseline. Strive for consistent, steady, incremental progress over time.\
Not trying means you fail immediately. It is not a good option.\
\
These are the five bullets which outline my intentions for creation. “Intentions” being the key word here - Unfortunately, I don’t always do everything I say I’m going to do.\
\ #Quotes [Lefie](./Lefie.md) #Rules\
\
\#1 this too shall pass\
\#2 security is a false belief\
\#3 simple pleasures bring the most happiness\
\#4 routines are a good thing\
\#5 a bit of risk makes me feel alive!\
\
\#Quotes #YT

#Quotes #Rules
