\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{From the half-light of dawn to the half-light of evening, the eyes of a leopard, in the last years of the twelfth century, looked upon a few wooden boards, some vertical iron bars, some varying men and women, a blank wall, and perhaps a stone gutter littered with dry leaves. The leopard did not know, could not know, that it yearned for love and cruelty, and the hot pleasure of tearing flesh, and a breeze with the scent of deer, but something inside it was suffocating and howling in rebellion, and God spoke to it in a dream: You shall live and die in this prison, so that a certain man may see you a certain number of times and never forget you and put your figure and your symbol into a poem, which has its exact place in the weft of the universe. You suffer captivity, but you shall have given a word to the poem.}\newthought{- 'Inferno, I, 32', by Jorge Luis Borges}}

\nolinenumbers
\smsleft{Hi Pengk, Tom Finnemore here. 
Why are the Aderhold couple annoyed, dear?}

\smsright{Good morning my Vicar,
Because I was annoying, sir}

\smsleft{Annoying how? Pray, tell}

\smsright{I was flirting with Adelle}

%\smsleft{...}

\smsright{Inviting myself to dinner, asking her out for coffee, slow-dancing with her, telling her to freely call me, texting her suggestive messages, and eating dessert from her hand, all in front of Dirk, her husband, her man.}

\smsleft{You did all these in front of Dirk,
But what's happened behind his back?}

\smsright{I told Adelle I love her, and day or night I want her}

\smsleft{Now why would you say that, Pengk?}

\smsright{To catch an adulterer. And there was something other
\vspace{1em}
She was matchmaking Sophia, her 19yo daughter, to me and I didn't want `her'.}

\smsleft{Ahh, I realise. 
Please apologise}

\linenumbers \vspace{2em}



