\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{Today marks the start of my 40-day introspection.}}

\vspace{-1.1cm}
\begin{fullwidth}

\newthought{[Nnamdi Azikiwe]}
It's your 500 naira zaddy, Nnamdi Azikiwe, here to say `Gengen Rap Battles of History'
Alhaji Atiku!\ \hspace{0.3cm} versus \hspace{0.3cm} Asiwaju Tinubu!\ \hspace{0.3cm} versus \hspace{0.3cm} Peter Obi! \hspace{0.3cm} BEGIN! \resetlinenumber[1]

\newthought{[Alhaji Atiku]}
My fellow Nigerians, una how far, I am Atiku D. Abubakar.\resetlinenumber[1]
Grand Commander of the Order of the Niger, Waziri Adamawa.
I possess the connections for this election - the things that Peter Obi needs and lacks.
I'm a Master’s holder in our nation’s \emph{away} relations, while Tinubu claims he’s not a quack.
Making good things happen - PDP - Power to the People
We are the party with structure - our democracy is a government for the people.
Oh, just because we did not play ball, Obi switched from PDP down to Labour.
This is not the first time he left us, and this will not be his final betrayal.
``Buhari's been a bad boy'', who put am?\ Make una blame Tinubu -
Ex Governor, Lagos should have sacked you!\ Ex Governor, Anambra sacked YOU!
I paid for this seat, you know it’s not free, I don't trust any of you, I trust me.
Step down and watch my ascendancy.\ What's that sound?\ I dey gidigba, no p.


\newthought{[Asiwaju Tinubu]}
My dia!\ This is what you do with internet freedom?\ldots\ Bars!\ -- You will soon be behind them.\resetlinenumber[1]
As the Christians resort to violence, I should get myself a Muslim VP
I paid for this seat, you know it’s not free.\ I must win this election, over my dead body
will I lose, if I use all of my councillors.\ I chase the applause, don't mind the cost!
Here's the world through my eyes; the Labour party currently has no officials to work with this guy
Meanwhile, I've got spies on the inside `nd they say PDP despises its bride.
Wike has started beef with the alleged commanders-in-chief.
The Naira nor dey fear me, na me be jagaban.
If na votes them dey sell, I pay triple for each one.
You dey ment?\ Abi na juju?\ It is now my turn - tell the people to vote for Tinubu.
Broom, broom, broom, broom, broom; Cockroaches get killed by broom.
A vote for me is a vote not wasted.\ You simply must - abi you wan COLLECT?


\newthought{[Peter Obi]}
Atiku and Tinubu, the ancients, see, our Nigeria is obidient.\resetlinenumber[1]
I am food for thought to the youth, I am not desperate to be president.
It's evident I am competent, I'm heaven-sent, and I'm passionate to see a Nigeria that works.
I risk not living to see our glory - you just want to be resident of Aso Rock.
Where has the party with “STRUCTURE” taken its people over the years?
I will remind you, good sirs who bribe in dollars, you are not secretaries of foreign affairs.
There will be a revolution in 2023.\ Go and ask the youth; they are here, they can see.
I will lay down my life if it sets us free from the APC/PDP stealing our PVCs.
Pay some attention - you don’t want to fail this exam.
Nigerian banks, come on, buy the new Nigerian brands.
And, if you must import, try and buy most of your foreign goods second-hand.
Chai, my guys, pack your kaya and fly oh, the cost of governance is too damn high oh.
\end{fullwidth}