\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{TBD \theproverbs}} \stepcounter{proverbs} %\marginnote[1mm]{\textit{?}}

\nolinenumbers
\begin{fullwidth}

    Onowu, I hope this letter finds you feeling well.
    \vspace{0.4cm}
    I've been blessed with some knowledge, from everlasting nature, that I must share with you.
    \vspace{0.4cm}
    I couldn't help but recognize the irony that the state named Delta doesn't yet have a dam for flood control.\ Instead, we
    have issues of flooding every year when Cameroonian authorities release water from Lagdo Dam into River Benue.
    \vspace{0.4cm}
    State Governor, Hon.\ Sheriff has approved the setting up of a Flood Disaster Management Committee to start ensuring
    government intervention.
    \vspace{0.4cm}

    \textbf{The Vision: A Positive Impact on Delta State}
    \vspace{0.4cm}
    I am writing to propose a preventative solution to the flooding issue.\ I have identified a potential opportunity in the
    abandoned Ogwashi-Uku dam project in Aboh Ogwashi, Aniocha South.\ Completed by the government in 2018/2019,
    the dam, situated along the Uyorfor River, presents an opportunity for private sector involvement through a concession
    agreement.
    \vspace{0.4cm}
    My proposal is to engineer this dam to provide reliable electricity, by pumping water into the dam with solar power
    during daylight hours, then discharging the water at a constant rate across the day, every day.\ This is basically a dam
    acting as a battery to ameliorate the irregular flow of solar power.\ The dam will store the excess electricity generated in
    the day, by pumping flood water into its reservoir, and releasing the hydroelectric power in the evening.
    \vspace{0.4cm}

    \textbf{The Mission: A Sustainable Solution for Flooding and Power Supply}
    \vspace{0.4cm}
    While this venture poses a considerable undertaking, with an estimated cost of \textnaira282,640,000, its feasibility is grounded
    in its long-term benefits.\ Unlike conventional lithium-ion solar batteries with limited lifespans, this hydroelectric
    solution offers sustainability and longevity, to keep on getting returns on investment.
    \vspace{0.4cm}
    If you were to spend that capital on lithium-ion solar batteries, they would only have a lifespan of up to 15 years or
    2500--3000 charge cycles \textendash whichever happens first.\ A photovoltaic inverter is only scalable for Delta State if we use
    rivers and lakes as the batteries.
    \vspace{0.4cm}

    \textbf{Investment Opportunity: Your Call To Action}
    \vspace{0.4cm}
    I am seeking your support to travel from Abuja to Asaba ASAP. And also your help to facilitate meetings with State
    Government officials about acquiring this concession.\ I plan to take advantage of the dam's potential to store and
    manage flood water, complemented by a nearby solar power plant.
    \vspace{0.4cm}
    I am confident you and your friends can support this rural electrification project.\ Your involvement will hold immense
    value because you are the great \textit{Anioma}.
    \vspace{0.4cm}
    This big battery will prove to be a good store of electricity for Aniocha, and be a good store of wealth for its investors.
    \vspace{0.4cm}

    Your speedy answer, will sincerely be ever gratefully received by
    \vspace{0.4cm}
    Your dutiful humble Son.

\end{fullwidth}
\linenumbers