\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{TBD \theproverbs}} \stepcounter{proverbs} %\marginnote[1mm]{\textit{?}}

Honoured Gatekeeper,

I hope this email comes to you at a time

when you are not so pressed by your own affairs that you'd conveniently decline

to read it.\ And please forgive me for writing such an email in rhyme,

I just wanted to captivate you to read each intricate line.

I am typing because you are in a need of a Project Engineer,

%and I possess the qualifications,

%and preferred experience in order to serve you there.

and I possess the qualifications and experience to serve you there.

%The only hurdle is that, first I would need to process a work visa
The only hurdle is that, first I would need a work visa

%since I'm a British-Nigerian Civil Engineer,
since I'm a British-born Nigerian-based Civil Engineer,

%currently in Abuja.

My name's Pengk Sylvester.

After graduating from university,

I was coached and mentored here by the Setraco company,

despite every other firm trying to poach my personality.

They fought over me.

I am aware of my high opinion of my character and circumstance,

I just seek not to conceal from you a worthy affair's beginnings.

It was evident to many that I am enthusiastic for optimized performances.

At Setraco, I got to practice fixing the constituent elements of many instruments,

and got to see the enormous complexities that help us to fulfill projects.

%I was their Civil Engineer with them before I started working for government officials.

The Nigerian \textit{Federal Capital Development Authority} taught me additional steps;

we've used trenching, and directional drilling to put water pipelines subsurface.

In similar respects,

I learned from the German \textit{Deutsche Vereinigung für Wasserwirtschaft, Abwasser}

\textit{und Abfall} in Düsseldorf, on implementing ORC for wastewater heat recovery.

Following all that, I now desire to contribute my energy to Fervo Energy,

and so I'm applying for this vacancy.

I've decided to approach you, the person with the authority to hire me,

with this letter to aforemention my benefits and hurdles properly.

I possess the qualifications, standards, and apprentice experience,

for me to harness

to serve your geothermal projects and/or lithium extraction investments.

I am a scholarly-trained black man in my very early twenties,

and to make important info rhyme is just my kind of kindness.

My focus is fully into civil engineering, not less.

I am the only one at the intersect

of these three things that I do best, I guess.

Rhyming, brine mining, and reliable engineering.

You can't get this anywhere else.

Hence, say yes to my humble request

to join you.\ Dear Hiring Manager, it makes perfect sense.

I look forward to receiving your correspondence.

Sincerest regards, P.S.