\mytitle{\thedaynumber/1001}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{}}

\textit{[WHICH PAIN IS MOST PAINFUL OF ALL?]}
\nolinenumbers
\begin{fullwidth}

\hspace{0.4cm}1.\ The pain of knowing you will die tomorrow.\ You've prayed that if your death could be avoided then let it be avoided,
\phantom{1. }but if it can't then let God's will be done.
2.\ The pain of being betrayed to death by a member of your household.\ One of your best friends sold you for 30 pieces
\phantom{2. }of silver.
3.\ The pain of your other household members denying knowing you while seeing you in custody.\ At least one of them
\phantom{3. }was recorded as denying you, their bestie, 3 times in one morning.
4.\ The pain of being flogged till your back is shredded and perspiring blood.
5.\ The pain of knowing you're innocent.\ You've been falsely accused by a powerful person.
6.\ The pain of knowing everyone else knows you're innocent and wrongfully accused, and yet join to kill you.
7.\ The pain of being condemned by a crowd of the very people you've spent your whole life dying to save.
8.\ The pain of watching a criminal be released instead of you.\ There is injustice when the innocent are punished with the
\phantom{8. }guilty, but when the guilty are set free for the innocent to die, that's evil.
9.\ The pain of having a crown of thorns pushed onto your head as a mockery of your situation.
10.\ The pain of dragging your own cross from Gethsemane to Golgotha.\ An innocent person wouldn't do it.\ A guilty
\phantom{10. }person still wouldn't do it.\ However, you did it to set a good example of endurance for other followers.
11.\ The pain of a mother watching her son die--but no, not just die--be murdered, and you cannot fight it.
12.\ The pain of your clothes stripped from your body, you are nailed to your cross, you are crucified, given vinegar to
\phantom{12. }drink instead of water, your ribs are pierced, and you can't breathe.
13.\ The pain of dying between two thieves so people think you're guilty.
14.\ The pain of forgiving everybody involved in the injustice.

\end{fullwidth}
\vspace{-1.5em}
\linenumbers