\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{The opposite of Faith isn't Doubt; it's Certainty.}}

\nolinenumbers
\begin{fullwidth}

Onowu sir, I pray you're having a good day.
\vspace{0.4cm}
Have you noticed what happens when the bike and keke customers form a crowd during rush hour?
\vspace{0.4cm}
The others see the line is too long, and they leave for another station.\ Time is everything to them.
\vspace{0.4cm}
That's why I'm now suggesting we create a Fuel Fast-Lane.
\vspace{0.4cm}
A system where bike riders don't wait at the pump at all.\ They simply pay, grab a pre-measured canister, go, and pour.
\vspace{0.4cm}

---
\vspace{0.4cm}
1.\ Safety \& Compliance \textemdash No ``Water Bottles''
\vspace{0.4cm}
Petrol in water bottles is a big no-no, as you know.\ That's why we do it with legal, fuel-approved 1L or 2L HDPE
canisters.\ Or those metal cans we see in movies, that have a built-in funnel spout.
\vspace{0.4cm}
We pre-fill the cans during off-peak hours, so we're not slowing the pumps.\ Seal them after filling to prevent
evaporation or contamination.\ Store in a ventilated rack away from heat and sparks.\ Brand them with our station name.
\vspace{0.4cm}
During rush hour: bike and keke riders buy canisters at a dedicated counter.\ Ensure stock is always ready.\ You keep
selling fuel, now faster, hence a higher volume.
\vspace{0.4cm}

---
\vspace{0.4cm}
2.\ The Rush-Hour Workflow
\vspace{0.4cm}
Off-Peak: Attendants fill canisters and seal them.
\vspace{0.4cm}
Rush Hour: bike riders skip the pump, pay at the counter, grab their canister, and go.
\vspace{0.4cm}
Optional Swap System: Riders can return empties for refilled ones, creating repeat business and keeping containers in
circulation.
\vspace{0.4cm}
---
\vspace{0.4cm}
So, let's imagine we buy 100 bottles.\ That means we can sell an extra 100 litres during a 2-hour rush and keep the
crowds small.\ Do that twice a day, seven days a week, we're adding over 6,000 litres a month.\ At even a modest margin,
this isn't small change, and we're now the fastest station in the area.
\vspace{0.4cm}
Faster service, happier riders, higher sales.\ We call it the Petrol In No-time Kiosks (PINKs).
\vspace{0.4cm}
Your dutiful humble Son.

\end{fullwidth}
\linenumbers