\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{To achieve great things, two things are needed; a plan, and not quite enough time.} \newthought{- Leonard Bernstein}}

\nolinenumbers \begin{fullwidth}
\newthought{- Letter for Prof Dadda}
We met each other during our weely NYSC CDS meeting. We like each other, and 
\
we started growing our lives in the same direction. After our youth service, she 
\
found a job in Lagos, and I found a job in East Africa.
\
Our jobs were avenues to be useful while earning money, and our ensuing long-distance relationship was a small 
\
sacrifice to pay for that. She relocated to Abuja, and I visited her there for a month earlier this year.
\
I invited her multiple times to come work for my employer, so that I could be near her again.
\
She's declined the position saying that my company is only a startup.
\
I tried to keep in touch online, to maintain open lines of communication.
\
But her work schedule and mine conflicted, with little room for coincidental leisure.
\
To further complicate matters, my time zone is two hours ahead of hers, meaning that even on the few mornings or 
\
evenings that she has for herself, it's my 10am work time or 10pm bedtime.
\
With some effort, we manage to have an average of 7 hours quality time together per week.
\
We chose to commit that time to a joint bible study, but that commitment proved unsustainable.
\
We are like two sailboats trying to keep in touch with each other on a roaring sea, but the tides keep pulling us apart.
\
We can only see glimpses of one another from afar, but cannot know what things are like for the other person.
\
There's not enough consistent overlap of free time.
\
The long-distance relationship has made communication less and less intimate, considering the circumstances.
\
The ability to live and work together would probably have the best chance at maximising information transfer and 
\
make for a more harmonious union. But we do not know how best to achieve that just yet.
\
I've offered to bring her to Tanzania for two weeks next year, if only to see the sights together during her leave of 
\
absence from work. But she's declining the offers. I'm at my wit's end, and that's why I've come to you, dear sir.
\
Please advise me, how may I help myself to sail these (and more) unhelpful tides, please pray for me.
\end{fullwidth}
\linenumbers
