\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{Inspired by \href{https://youtu.be/I-iyGGPabpI?t=8591}{\textcolor{blue}{Eric Weinstein}}}}

The songs of Tom Lehrer are pretty terrific satiric music.

And Pablo Casal's renditions of Bach's suites will help you think.

You might want to explore the Tanzanian Serengeti safari.

One of the least complex languages to learn is Swahili.

Find a recipe book, and make sure that you visit

every meal in there, whether you cook it or not.

Consider indulging in some classical books,

there's always a reason they were once called classics.

On a walk, take a serious listen to Snarky Puppy

playing Lingus from their album We Like It Here.

I think the musical Hamilton is one of the most

beautifully / brilliantly composed album of poems.

It's absolutely inspiring.\ And if you really like it,

Kendrick Lamar has an album called Good Kid Maad City.

Seriously think about visiting famous parts of the world.

Some places are an overrated tourist-infested bore \sidenote[1]{(cough) Paris},

and some will have a life-changing effect on you too.

Take a look at Jreg's channel and his videos on youtube,

He's making amazing stuff being done by no one else on earth.

I think that Ed Sheeran is really amazing.\ And that's a fact.

Have a listen to his version of Love Yourself by Justin Bieber.

That's one song I didn't really appreciate when I was younger.

I think that The Wire was imbued with a lot of wisdom for you.

And it blew my mind open when I saw it at the tender age of 22.

I have my creative outlets to make myself laugh or cry.

Get married.\ It may not work out.\ At least give it a try.

Raise some kids, it's the best gift that will keep on giving.

Try to keep this thing we have -- this human race thing going.

Dream big about legacy.\ Don't feel embarrassed to fail.

Conquer the world or leave a permanent you-shaped stain.

Do the hardest, most technical thing you possibly can do.

And be prepared to use that facility in different ways than you

are honing it.\ Train.\ Get good on a bunch of different stuff.

Learn to think across disciplines.\ Get involved with a church.

Wish your country's leadership well.\ Even if you didn't vote for them,

They've got hard work to do, even if you think they're horrible men.

Be good to each other.\ Let your neighbour's pain be yours.

And make sure you have some fun before it's lights out.