\mytitle{\thedaynumber/\death}
\hypertarget{\the\value{daynumber}}

\marginnote[1mm]{\textit{}}

\newthought{- Marvelene}
\resetlinenumber[1]
I have reached a decision, I wish to call off our engagement.

I reached this decision while throwing back to a bunch of events.
The two engagement rings I've worn, I bought them myself and placed them on my ring finger. It never felt right to me, and you never did what you said of replacing it when you got back.

No.2 I noticed the ring has been kinda a roadblock to me. I gained more by appearing young and single. There's a "Single" status advantage that's brings me tangible and intangible benefits rather than being engaged. For a year plus I've been experiencing that.

No.3 your family. You're the first born from the wealthiest member of your father's extended family, and the firstborn of the first born maternally. You also have a step mother who requires a lot of your attention. You're also a kind soul who is ready to be off help to his uncles and aunts most of the time. Sorry to say this, but family-dynamic-wise, you're not my type. I'm an elusive one, and you're the opposite. It is your wish to be, but you're not exactly in a position to.

Then there's the recent fiasco about your Boss dying which I was genuinely worried about you and your Tanzanian work. After reviewing that event, I decided that you were not ready to meet my parents anytime soon. I feel you're not ready for this family merging event which is kinda what marriage is about.

And for now, my interest in marriage has been lost. I don't see the appeal in it anymore. It was there when I needed a good reason to move States for my job.

I don't mind dating for a long time, but I do mind staying engaged. It hasn't been beneficial so far.

In summary, since we're not planning anything and we haven't moved past just rings and titles, I'd like us to revert to being in a dating relationship, cos that's how it feels. When you're ready, aligned with your family and also financially independent, then maybe we can upgrade again.

\vspace{4em}

\marginnote[1mm]{\textit{To forgive is divine.}}
\newthought{- Pengk}
\resetlinenumber[1]
hello