\begin{fullwidth}

\section{I Know Another One}

\vspace{0.5cm}
\hyperlink{565%575
}{\textcolor{red}{Click here to scroll to \today.}}
\vspace{1cm}

This is my anthology of over 1001 original poems in various meters, which I wrote over 1001 days - Between 19-Sep-2022 and 15-Jun-2025.\ I wrote these poems - these thoughts - for the purposes of wooing a woman, and also to show the young ones how wooing could be done.
%I wrote these poems - these thoughts - for the purposes of wooing the mother of my kids (I'm a hopeless romantic), and also to show the young ones how wooing could be done.


This book will run through a series of scenes for me - some of them are funny, some fictional, some heretical, and some are a bit weird - and are for me to know how I feel about these things.
Some of my poems are possibly poetry from the perspectives of popular persons.

Contrary to conventional self-help books, I, the author here, am both the teacher and the student.\ I am both the enlightener and the moron.
I am the performer \textbf{and} the audience to the theatre of my imagination.

My assumed audience is rap enthusiasts.\ That subgroup of people who have used some internet time to listen to rap.

Viewer's discretion is advised.


\vspace{2cm}
My personal favorites:
\begin{multicols}{4}
\begin{itemize}
    \item \hyperlink{99}{2022- Dec- 26}
    \item \hyperlink{104}{2022- Dec- 31}
    \item \hyperlink{171}{2023- Mar- 8}
    \item \hyperlink{300}{2023- Jul- 15}
    %\item \hyperlink{}{}
    %\item \hyperlink{}{}
\end{itemize}
\end{multicols}


\vspace{2cm}
Cathartic confessions:
\begin{multicols}{4}
\begin{itemize}
   \item \hyperlink{49}{2022- Nov- 6}
   \item \hyperlink{67}{2022- Nov- 24}
   \item \hyperlink{251}{2023- May- 27}
   \item \hyperlink{277}{2023- Jun- 22}
   %\item \hyperlink{}{}
\end{itemize}
\end{multicols}


%\vspace{1cm}
%
%\begin{multicols}{4}
%\begin{itemize}
%   \item \hyperlink{}{
%   \item \hyperlink{}{
%   \item \hyperlink{}{
%\end{itemize}
%\end{multicols}


%\vspace{1cm}
%
%\begin{multicols}{4}
%\begin{itemize}
%   \item \hyperlink{}{
%   \item \hyperlink{}{
%   \item \hyperlink{}{
%\end{itemize}
%\end{multicols}


\vspace{2cm}
Not Safe For Work (NSFW) raunchy poems:
\begin{multicols}{4}
\begin{itemize}
    \item \hyperlink{28}{2022- Oct- 16}
    \item \hyperlink{47}{2022- Nov- 4}
    \item \hyperlink{109}{2023- Jan- 5}
    \item \hyperlink{432}{2023- Nov- 24}
    %\item \hyperlink{}{202- - }
    %\item \hyperlink{}{202- - }
    %\item \hyperlink{}{202- - }
    %\item \hyperlink{}{202- - }
\end{itemize}
\end{multicols}

\newpage \thispagestyle{empty}
~\vfill
\begin{doublespace}
\noindent\fontsize{18}{22}\selectfont\itshape
\nohyphenation
My thanks go to;\\
Annabelle for softening my heart,\\
Catherine for requesting my poetry,\\
Hibatullah for enduring my love,\\
Marvelene for being my soulmate,\\
Mydear, Ify, Sylvester,\\
Gill, Will, and Lin-Manuel Miranda.
\end{doublespace}
\vfill
\vfill

\end{fullwidth}

\blankpage
\newpage \linenumbers  