%\newpage \thispagestyle{empty}

\blankpage
\fancyhf{}
\nolinenumbers

\begin{fullwidth}

%% Roll Pearsall-esque credits

{\centering{\Huge Credits}
\vspace{1cm}

\newthought{Author -- Pengk Sylvester}

\newthought{Editor -- Pengk Sylvester}

\newthought{illustrator -- Pengk Sylvester}

\newthought{This or That -- Pengk Sylvester}

\newthought{The Other -- Pengk Sylvester}

\newthought{Word Processor -- \latex{}}

\newthought{Compiler -- JetBrains IDE}

\newthought{Type of JetBrains IDE -- IntelliJ IDEA 2023.3.2 (build IC-233.13135.103)}

\newthought{Operating System -- Windows 11.0 (amd64)}

\newthought{TeXiFy IDEA version -- 0.9.2}

%\newthought{ -- }

%\newthought{ -- }

%\newthought{ -- }
}

\newpage \blankpage

%% Footnotes. Please keep it to a maximum of eight lines each.
{\Huge Notes on Some of the Poems}
\vspace{1cm}


\newthought{\hyperlink{1}{\textbf{2022- Sep- 19:}}}\\
This is the very first poem.\ I started this book to woo a woman named Hiba, and I pivoted away from her when I fell in love with my best friend, my soulmate, my Marvelene.


\newthought{\hyperlink{28}{\textbf{2022- Oct- 16:}}}\\
This is a true story.\ My sister, Perfect, was raped multiple times over many years by a family friend, Ozioma, who was responsible for looking after us as children.
I had felt powerless to save my own sister, and I wish I knew how to report him.

\newthought{\hyperlink{29}{\textbf{2022- Oct- 17:}}}\\
`Give two cents' is a colloquial term for `give advice'.


\newthought{\hyperlink{52}{\textbf{2022- Nov- 9:}}}\\
\ldots


%\newthought{\hyperlink{}{\textbf{:}}}\\
%This was inspired by Fragile Dogubo`s piece Breakfast`.


\newthought{\hyperlink{97}{\textbf{2022- Dec- 24:}}}\\
This poem is about Christmas capitalism.

\newthought{\hyperlink{108}{\textbf{2023- Jan- 4:}}}\\
This is a calligram made of haikus.\ A calligram is a poem where the body of the text is laid out in such a way as to create a silhouette-like image.\ A haiku is a short form of Japanese poetry composed of only 17 syllables in a 5, 7, 5 pattern.


\newthought{\hyperlink{110}{\textbf{2023- Jan- 6:}}}\\
The wife's requests are logical loops with two meanings.\ The husband in the poem will end up buying a dozen loafs of bread because the store had eggs, hence fulfilling the wife's conditional statement.


\newthought{\hyperlink{123}{\textbf{2023- Jan- 19:}}}\\
Instead of an eight-line poem, I've opted here for an eight-word blackout poem.


\newthought{\hyperlink{127}{\textbf{2023- Jan- 23:}}}\\
I had wrongly calculated the end date in \hyperlink{93}{Poem 93/1001}.\ I've corrected it in said poem.\\
`Sou desu ka' is Japanese for `I see'.


\newthought{\hyperlink{132}{\textbf{2023- Jan- 28:}}}\\
Aflattus is a Greek word meaning the impulse of creative power or inspiration, especially in poetry, considered to be of divine origin.


\newthought{\hyperlink{144}{\textbf{2023- Feb- 9:}}}\\
The Notorious B.I.G.~did a countdown-themed rap called `10 Crack Commandments', and Lin Manuel Miranda did it next for me with a musical number called `10 Duel Commandments'.


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


%\newthought{\hyperlink{}{\textbf{:}}}\\


\newthought{\hyperlink{1000}{\textbf{2025- Jun- 14:}}}\\
\ldots

\end{fullwidth}